\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{setspace,mathtools,indentfirst}

\doublespacing{}

\begin{document}
\noindent Nelson Batista, Max Inciong, and Francesca Truncale

\noindent Senior Project II --- Fall 2017

\noindent Professor Jianting Zhang

\noindent Report for Sept. 12


Our project is going to be based on sub-graph isomorphism. Our plan is to take Twitter data and create recommended groups based on a shared interests. For example, if 2 people like the same 10 accounts, it would notify them and recommend that they follow each other, if they don't already. If more than 2 people like the same 10 accounts, it would notify them of the others that like them and suggest forming a ``friend group.''

We have at our disposal a graph that tracks people's ``mentions,'' which refers to the act of one person mentioning another. This is done by prefacing the other person's name with an ``at'' sign (@). Our plan is to track multiple people mentioning the same few accounts. From this, we can create a subgraph and compare it to the entire graph of mentions to see how many times our subgraph appears. For example, if person A mentions accounts 1 through 10, we have to find other people who like the same 10 accounts.
If only one person, B, likes the same 10 accounts, then it recommends to A to follow B, and vice versa. If multiple people, B, C, and D, like the same things as A, and they do not currently follow each other, recommend a friend group/social circle.

The project's progress should proceed as follows. Each week will be accompanied with a report detailing the actual progress.

\begin{itemize}
  \item September 12th --- This report, along with the data set that will be used to test our solution, both for correctness and for performance benchmarks.
  \item September 19th --- Report on plans to implement our solution, as well as progress on development of the solution itself.
  \item September 26th --- Completion of program to match % MAAAAAX
    % maybe completion of CPU implementation?
  \item October 3rd --- % MAAAAAX
  \item October 10th --- Verification that solution works on data set provided, begin planning GPU implementation.
    % these next two are a crapshoot
  \item October 17th --- Begin work on GPU implementation, with focus on optimizing speed of mapping nodes from one graph to another.
  \item October 24th --- Continue working on GPU implementation, shifting focus to comparing connections between nodes and checking for isomorphism.
  \item October 31st --- Report on bugs identified and plans to fix them.
  \item November 7th --- Completion of GPU implementation. 
  \item November 14th --- Designing of GUI/front end.
  \item November 21st --- Continuing work on front end.
  \item November 28th --- Connection of front end to back end.
  \item December 5th --- Completion of project, final testing.
  \item December 12th --- Completion of final report.
\end{itemize}

\end{document}

